\chapter*{General Introduction}
\addcontentsline{toc}{chapter}{Introduction G\'en\'erale}

Nowadays, public-private partnership is an increasingly popular procurement option used by governments over the world for multi-faceted project delivery. PPP is a cooperative venture between the public and private sectors for the delivery of a public service through appropriate allocation of resources, risks and rewards.
\vskip 0.5cm
The evolution of ChatGPT has significantly impacted the world of work, revolutionizing communication and collaboration in the workplace. As an advanced language model, ChatGPT has transformed how professionals interact with technology, enabling more efficient and natural language-based interactions. With its ability to generate human-like responses and provide contextually relevant information, ChatGPT has become an invaluable tool for streamlining various work processes.
\vskip 0.5cm
Using ChatGPT in public-private partnership work has indeed proven to be beneficial in various ways. By leveraging ChatGPT's capabilities, organizations like Jade-Advisory can effectively communicate large volumes of data and documents, resulting in significant time savings and improved efficiency. Additionally, ChatGPT can be utilized to assess project feasibility by analyzing and interpreting complex information, thereby facilitating informed decision-making.
\vskip 0.5cm
By leveraging productivity improvements, Jade-Advisory has recognized the significance of integrating AI assistance for its repetitive work processes. This integrated AI assistance enables the organization to efficiently communicate with its extensive data and generate documents. The use of AI not only streamlines repetitive tasks but also enhances the overall productivity and accuracy of document generation. This approach allows Jade-Advisory to focus on more complex and strategic initiatives while ensuring that its data is effectively utilized to produce high-quality documents.
\vskip 0.5cm
In this context , we want to share our final company-suggested project as well as the process that led to its realization. Our goal for this project is to create a simple and easy-to-use app. It will have a conversational ai assistance and will be used for making reports, evaluating projects, and managing resources. We're excited to share this user-friendly solution with you.


